Introduction

### 2015-07-19 dissertation/motivation.tex
All references so far

Technically, it might be an easier problem to solve if the data could
be centralized, and that solution has been argued by
\cite{DBLP:conf/semweb/BetzGHS12}. Nevertheless, even if all their
arguments remain valid from a technical viewpoint, the most important
arguments against centralisation are social: If important components
of the Semantic Web is under the control of some central authority, it
is likely that one cannot publish anything, link to anything, or
develop any application without permission. It may create an unhealthy
power structure, which may create commercial or intellectual
hegemonies. Tim Berners-Lee discussed this in \cite{TODO} and an
interview in Wired Magazine in 2014\footnote{see
  \url{http://www.wired.co.uk/news/archive/2014-02/06/tim-berners-lee-reclaim-the-web}}
This is the key motivation to still design a distributed Semantic Web,
regardless of the technical difficulties that may arise.

@@

It is also important to frame the question correctly: We want to
answer queries, we do not require that any remote server accepts the
entire burden of evaluating queries. It is becoming quite clear that
the current practice of evaluating any arbitrary SPARQL query on a
remote server is economically unsustainable, and it is made clear by
the instability of SPARQL endpoints on the Web \cite{TODO}.

>>>>

Technically, it might be an easier problem to solve if the data could
be centralized, and that solution has been argued by
\cite{DBLP:conf/semweb/BetzGHS12}. Nevertheless, even if all their
arguments remain valid from a technical viewpoint, the most important
arguments against centralisation are social: If important components
of the Semantic Web is under the control of some central authority, it
is likely that one cannot publish anything, link to anything, or
develop any application without permission. It may create an unhealthy
power structure, which may create commercial or intellectual
hegemonies. Tim Berners-Lee discussed this in \cite{berners2000weaving} and an
interview in Wired Magazine in 2014\footnote{see
  \url{http://www.wired.co.uk/news/archive/2014-02/06/tim-berners-lee-reclaim-the-web}}
This is the key motivation to still design a distributed Semantic Web,
regardless of the technical difficulties that may arise.

@@

It is also important to frame the question correctly: We want to
answer queries, we do not require that any remote server accepts the
entire burden of evaluating queries. It is becoming quite clear that
the current practice of evaluating any arbitrary SPARQL query on a
remote server is economically unsustainable, and it is made clear by
the instability of SPARQL endpoints on the Web \cite{buil2013sparql}.

### 2015-07-19 dissertation/related.tex
All references so far

Verborgh et al. \cite{ldf1} share many of the observations and goals
that motivates this study. They introduce a hypermedia system that can
be used to answer individual triple patterns (known as Triple Pattern
Fragments (TPF)). Their stated goal is to transfer as much as possible
of the burden of evaluating a query from the server to the
client. This can happen because a simple pattern match for a single
triple pattern need not have a SPARQL parser, nor a query
planner. Moreover, the server may materialise responses to frequent
triple patterns and store them in a file system, which can be managed
by a simple Web server. The results may also be paged, so that each
individual response may be kept small. However, TPF mandates that
every response must contain a cardinality estimate for every triple
pattern, an operation that may be quite expensive for the server, and
indeed, this information may be so expensive to provide that SPARQL
planners may not provide it to keep the cost of planning itself
down. In \cite{TODO}, they demonstrated SPARQL evaluation over TPF,
and further improvements have been made in more recent papers.

Olaf Hartig has a large number of papers that are adjacent to the
present work, including his Ph.D. dissertation \cite{TODO} where he
explores querying Linked Data, i.e. query data that is not contained
in an a-priory defined collection of RDF data, but where a resources
are traversed to compute a result. Hartig provides solid formal
foundations for such query processing, as well as computational
feasibility, soundness and completeness. The most relevant paper of
this work is \cite{TODO}.

Acosta et al. \cite{TODO} has ongoing work named ``SHEPHERD'' to
create a SPARQL processor that takes into account observations done by
the SPARQLES survey \cite{TODO}, to decompose a SPARQL query into
subqueries that is indicated to be easier for the server to evaluate,
and so is well aligned with our goal to ease the load of the
server. It is not quite clear from the brief description in 
\cite{TODO} whether the SHEPHERD system can cache results locally.

>>>>

Verborgh et al. \cite{ldf1} share many of the observations and goals
that motivates this study. They introduce a hypermedia system that can
be used to answer individual triple patterns (known as Triple Pattern
Fragments (TPF)). Their stated goal is to transfer as much as possible
of the burden of evaluating a query from the server to the
client. This can happen because a simple pattern match for a single
triple pattern need not have a SPARQL parser, nor a query
planner. Moreover, the server may materialise responses to frequent
triple patterns and store them in a file system, which can be managed
by a simple Web server. The results may also be paged, so that each
individual response may be kept small. However, TPF mandates that
every response must contain a cardinality estimate for every triple
pattern, an operation that may be quite expensive for the server, and
indeed, this information may be so expensive to provide that SPARQL
planners may not provide it to keep the cost of planning itself
down. In \cite{verborgh2014querying}, they demonstrated SPARQL evaluation over TPF,
and further improvements have been made in more recent papers.

Olaf Hartig has a large number of papers that are adjacent to the
present work, including his Ph.D. dissertation \cite{hartig2014querying} where he
explores querying Linked Data, i.e. query data that is not contained
in an a-priory defined collection of RDF data, but where a resources
are traversed to compute a result. Hartig provides solid formal
foundations for such query processing, as well as computational
feasibility, soundness and completeness. The most relevant paper to
this work is \cite{hartig2011caching}.

Acosta et al. \cite{acosta2014shepherd} has ongoing work named ``SHEPHERD'' to
create a SPARQL processor that takes into account observations done by
the SPARQLES survey \cite{buil2013sparql}, to decompose a SPARQL query into
subqueries that is indicated to be easier for the server to evaluate,
and so is well aligned with our goal to ease the load of the
server. It is not quite clear from the brief description in 
\cite{acosta2014shepherd} whether the SHEPHERD system can cache results locally.
